---
title: "Seminar 6"
output: html_notebook
---

```{r}
library(sna)
library(igraph)
library(network)
library(intergraph)
library(NetCluster)
```

```{r}
load("advice_data_frame.Rdata")
load("friendship_data_frame.Rdata")
load("reports_to_data_frame.Rdata")
```

```{r}
head(advice_data_frame)
```

```{r}
head(friendship_data_frame)
```

```{r}
head(reports_to_data_frame)
```

Make an array of 3 the 3 data frames, add names to objects in list and check how many elements there are in our krack dataset

```{r}
krack <- list(advice_data_frame,
              friendship_data_frame,
              reports_to_data_frame)
graphs <- c('advice', 'friendship', 'reports')
names(krack) <- graphs
length(krack)
```

```{r}
names(krack)
```

```{r}
for (i in 1:length(krack)){
krack[[i]] <- as.matrix(krack[[i]])
}
```

```{r}
for(i in 1:3){
krack[[i]] <- subset(krack[[i]],
(krack[[i]][,3] > 0 ))
}
dim(krack[[1]]) # What is the size now?
```

```{r}
head(krack[[1]])
```

```{r}
for (i in 1:3){
krack[[i]] <- network(krack[[i]],
matrix.type = 'edgelist',
vertex.attr = list("AGE","TENURE","LEVEL","DEPT"),
vertex.attrnames = list("AGE","TENURE","LEVEL","DEPT"))
}
advice <- krack$advice
friendship <- krack$friendship
reports <- krack$reports
```

```{r}
friendship
```

```{r}
advice
```

```{r}
reports
```

Create a set of coordinates to run the plot in and plot networks

```{r}
n<-network.size(advice)
v1<-sample((0:(n-1))/n) #create a vector of random numbers
v2<-sample(v1)
x <- n/(2 * pi) * sin(2 * pi * v1)
y <- n/(2 * pi) * cos(2 * pi * v2)
mycoord <- cbind(x,y)
par(mar=c(0,0,1,0))
par(mfrow=c(1,3))
plot(advice, edge.col='azure4', vertex.col='darkorange',
     vertex.border='azure4',vertex.cex=2,coord=mycoord,
     main ='Advice')
plot(friendship, edge.col='azure4', vertex.col='darkorange',
     vertex.border='azure4',vertex.cex=2, coord=mycoord,
     main ='Friendship')
plot(reports, edge.col='azure4', vertex.col='darkorange',
     vertex.border='azure4',vertex.cex=2, coord=mycoord,
     main='Direct Reports')
```
Assignment task 1

1. Dyad census

```{r}
advice_dyad <- sna::dyad.census(advice)
friend_dyad <- sna::dyad.census(friendship)
reports_dyad <- sna::dyad.census(reports)
dyad_census <- rbind(advice_dyad, friend_dyad, reports_dyad)
row.names(dyad_census) <- c('advice', 'friendship', 'reports')
as.data.frame(dyad_census)
```

The networks are now positioned in a way to represented the networks from most to least connected, first being 'advice' and 'reports' being last

2. Centrality

a) Degrees
Creating igraph objects for further calculations

```{r}
advice_graph <- graph_from_data_frame(advice, directed = TRUE)
friend_graph <- graph_from_data_frame(friendship, directed = TRUE)
reports_graph <- graph_from_data_frame(reports, directed = TRUE)
```

```{r}
advice_indegree <- igraph::degree(advice_graph, mode = 'in')
advice_outdegree <- igraph::degree(advice_graph, mode = 'out')
advice_total <- igraph::degree(advice_graph, mode = 'total')
advices <- cbind(advice_indegree, advice_outdegree, advice_total)

friend_indegree <- igraph::degree(friend_graph, mode = 'in')
friend_outdegree <- igraph::degree(friend_graph, mode = 'out')
friend_total <- igraph::degree(friend_graph, mode = 'total')
friends <- cbind(friend_indegree, friend_outdegree, friend_total)

reports_indegree <- igraph::degree(reports_graph, mode = 'in')
reports_outdegree <- igraph::degree(reports_graph, mode = 'out')
reports_total <- igraph::degree(reports_graph, mode = 'total')
reports_d <- cbind(reports_indegree, reports_outdegree, reports_total)

as.data.frame(advices)
as.data.frame(friends)
as.data.frame(reports_d)
```

b) Betweenness

```{r}
advice_b <- igraph::betweenness(advice_graph)
friend_b <- igraph::betweenness(friend_graph)
reports_b <- igraph::betweenness(reports_graph)
all_betweenness <- cbind(advice_b, friend_b, reports_b)
colnames(all_betweenness) <- c('advice', 'friendship', 'reports')
as.data.frame(all_betweenness)
```

c) Closeness

```{r}
advice_closeness <- igraph::closeness(advice_graph, mode = 'all')
friend_closeness <- igraph::closeness(friend_graph, mode = 'all')
reports_closeness <- igraph::closeness(reports_graph, mode = 'all')
all_closeness <- cbind(advice_closeness, friend_closeness, reports_closeness)
colnames(all_closeness) <- c('advice', 'friendship', 'reports')
as.data.frame(all_closeness)
```

3. Triad census

```{r}
advice_triad <- sna::triad.census(advice)
friend_triad <- sna::triad.census(friendship)
reports_triad <- sna::triad.census(reports)
triad_census <- rbind(advice_triad, friend_triad, reports_triad)
row.names(triad_census) <- c('advice', 'friendship', 'reports')
as.data.frame(triad_census)
```

4. Transitivity

```{r}
#gtrans(dat, g=NULL, diag=FALSE, mode="digraph", measure = c("weak", 
 #   "strong", "weakcensus", "strongcensus", "rank", "correlation"), 
  #  use.adjacency = TRUE)

advice_weak <- gtrans(advice, mode = 'weak')
advice_strong <- gtrans(advice, mode = 'strong')
advice_weakcensus <- gtrans(advice, mode = 'weakcensus')
advice_strongcensus <- gtrans(advice, mode = 'strongcensus')
advice_rank <- gtrans(advice, mode = 'rank')
advice_corr <- gtrans(advice, mode = 'correlation')
advice_transitivity <- cbind(advice_weak, advice_strong, advice_weakcensus, advice_strongcensus, advice_rank, advice_corr)

fr_weak <- gtrans(friendship, mode = 'weak')
fr_strong <- gtrans(friendship, mode = 'strong')
fr_weakcensus <- gtrans(friendship, mode = 'weakcensus')
fr_strongcensus <- gtrans(friendship, mode = 'strongcensus')
fr_rank <- gtrans(friendship, mode = 'rank')
fr_corr <- gtrans(friendship, mode = 'correlation')
friend_transitivity <- cbind(fr_weak, fr_strong, fr_weakcensus, fr_strongcensus, fr_rank, fr_corr)

reports_weak <- gtrans(reports, mode = 'weak')
reports_strong <- gtrans(reports, mode = 'strong')
reports_weakcensus <- gtrans(reports, mode = 'weakcensus')
reports_strongcensus <- gtrans(reports, mode = 'strongcensus')
reports_rank <- gtrans(reports, mode = 'rank')
reports_corr <- gtrans(reports, mode = 'correlation')
reports_transitivity <- cbind(reports_weak, reports_strong, reports_weakcensus, reports_strongcensus, reports_rank, reports_corr)

as.data.frame(advice_transitivity)
as.data.frame(friend_transitivity)
as.data.frame(reports_transitivity)

all<-rbind(advice_transitivity, friend_transitivity, reports_transitivity)
colnames(all) <- c('weak', 'strong', 'weak census', 'strong census', 'rank', 'correlation')
row.names(all) <- c('advice', 'friendship', 'reports')
as.data.frame(all)
```

